drivers response diversity

### 2024-07-08 drivers_response_diversity.Rmd
new plots 3 and 4 for both dissimilarity and divergence

# second lm for maximum phosphorus ~ species richness
lm2 <- lm(mean_rdiv ~ Phos_max + sum_species, data = df_lm_excl)

@@

###Divergence figure 3

```{r}
# first lm for species richness ~ maximum phosphorus

>>>>

# pltting the first linear regression
lm1_plot <- bind_model1 |> 
  ggplot(aes(sum_species, fit,  color = category, fill = category)) +
  geom_line(linewidth = 1.2) +
  geom_ribbon(aes(ymin = (fit - se.fit), ymax = (fit + se.fit)),  alpha = 0.3, color = NA) +
  theme_classic(base_size = 20) +
  ylab("Mean dissimilarity") +
  xlab("Species richness") +
  # ylim(1,3) +
  scale_fill_manual(values = mycolor, aesthetics = c("color", "fill"), guide = NULL)

# Lms for all categories: endemic, translcated, non_native and non_endemic_native
# with data on all lakes
# Endemic
lm_endemic <- lm(mean_rdiv ~ endemic, data = df_lm)

plot_all_lms
# save as TIFF
# tiff(paste("total_models/plots/lm_all.tiff", sep = ""), units="in", width=11, height=7, res=300)
# # plot(ggarrange(depth1, depth2, ncol = 2))
# # plot science discussion
# plot(plot_all_lms)
# 
# dev.off()

###Figure 4
```{r}
```

###Figure 3 Divergence

```{r}

# Lms for all categories: endemic, translcated, non_native and non_endemic_native
# with data on all lakes
# Endemic
deriv_lm1 <- lm(mean_sign ~ endemic, data = df_lm)

# save as TIFF
# tiff(paste("total_models/plots/lm_divergence_all.tiff", sep = ""), units="in", width=11, height=7, res=300)
# # plot(ggarrange(depth1, depth2, ncol = 2))
# # plot science discussion
# plot(lm_divergence_all)
# 
# dev.off()
```

```{r}
# second lm for maximum phosphorus ~ species richness
lm2 <- lm(mean_rdiv ~ Phos_max + sum_species, data = df_lm_excl)

@@

###Divergence figure 4

```{r}
